ManuscriptFigures

### 2024-03-04 Code/ManuscriptFigures.Rmd
Added letters to overlay plot

 theme(#strip.text = element_blank(),

@@

        panel.grid.major = element_blank())

@@

ggsave(file = file.path(PlotsOut, paste("OverlayPlots",".tiff",sep = "")), plot = OverlayPlots, device = NULL, scale = 1, height = 25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

>>>>

 theme( strip.text = element_text(size = 13),

@@

        panel.grid.major = element_blank(),
        tagger.panel.tag.background = element_blank()) +
  tagger::tag_facets(tag_levels  = c("A", "I"), tag_suffix = "")

@@

# ggsave(file = file.path(PlotsOut, paste("OverlayPlots",".tiff",sep = "")), plot = OverlayPlots, device = NULL, scale = 1, height = 25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
